Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-07-27 paper/amia.tex
Auto Update from local Sharelatex

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

@@

\textit{There are many barriers to data access and data sharing, especially in the domain of computational research on health care data. Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility. We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to real data but lacks sensitive information. This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project. Kung Faux Pandas is an open source publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system that lowers barriers to HIPAA- and GDPR-compliant data sharing for enabling reproducibility and other purposes.}

@@

As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability. To further the aim of reproducibility we have provided our code and a sample of a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.

>>>>

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    citecolor=blue
}

@@

\textit{There are many barriers to data access and data sharing, especially in the domain of computational research using health care data. Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility. We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to real data but lacks sensitive information. This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project. Kung Faux Pandas is an open source publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system that lowers barriers to HIPAA- and GDPR-compliant data sharing for enabling reproducibility and other purposes.}

@@

As the data generated through KFP has no protected component, it can be shared along with code or methods to improve reproducibility as well as aid in replicability. To further the aim of reproducibility we have provided our code and a randomly generated dataset for testing purposes through our GitHub repository in a range of formats: Python environment files (conda and pip) to allow others to start with the same software libraries and specific versions that we used, a Docker container with code and sample data installed and already configured, and all source code along with version history so others can follow our development process.
